\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=2.5cm}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{listings}

\title{GQRVP: A Verifiable Epistemic Evolution Framework for Adversarial Multi-Agent Systems with Temporal Consensus and Cryptographic History}

\author{
  Gravit Network Team \\
  Grok (xAI) Integration Team \\
  \texttt{contact@gravit.network}
}

\date{April 2026}

\begin{document}

\maketitle

\begin{abstract}
We introduce GQRVP, a formal framework for verifiable epistemic evolution in adversarial multi-agent environments. Knowledge is modelled as a temporal graph $\Omega$, continuously updated through hypothesis generation, adversarial stress-testing, and weighted consensus over VRF-selected committees. A cryptographically anchored History Keeper ensures immutability of temporal states via hash-chained records and Merkle-based verification.

GQRVP is LLM-agnostic and supports seamless integration with multiple large language models including Grok, Claude, GPT-4o, Gemini, Llama, Mistral, and local models via Ollama. We present the formal model, theoretical properties, reference implementation, and five live integration tests demonstrating real-world adversarial resilience.
\end{abstract}

\section{Introduction}
Modern AI systems lack verifiable history of reasoning. Blockchains record transactions but not meaning. Multi-agent systems rarely provide strong verification of epistemic evolution under attack.

GQRVP solves this by creating a system where knowledge is not merely stored, but continuously validated, stressed, and re-anchored under adversarial conditions.

\section{System Overview}
The system is defined as:
\[ S = (\Omega, H, VRF, C, R) \]
where $\Omega$ is the epistemic graph, $H$ the History Keeper chain, $VRF$ the committee selection, $C$ the consensus function, and $R$ the reputation system.

\section{Multi-LLM Integration}
GQRVP is designed to work with any large language model. A universal Python SDK allows seamless integration:

\begin{lstlisting}[language=Python]
result = sdk.evolve_from_llm(
    llm_provider="claude",
    hypothesis="Your hypothesis here...",
    model_name="claude-3-opus-20240229"
)
\end{lstlisting}

Supported providers include Grok (xAI), Claude (Anthropic), GPT-4o (OpenAI), Gemini (Google), Llama, Mistral, and any local model via Ollama. This enables organizations to keep their preferred LLM while obtaining verifiable, immutable, and adversarially-robust outputs through Gravit.

\section{$\Omega$ Model}
$\Omega_t = (G_t, E_t)$ where nodes are hypotheses and edges are transformations: SUPPORT, CONFLICT, SUPERSEDE, TEMPORAL.

\section{History Keeper \& Merkle Chain}
Each state is anchored:
\[ A_t = H(G_t, A_{t-1}) \]
with Merkle root embedded for partial verification.

\section{VRF Committee Selection}
\[ C_t = \{ n_i \mid \text{VRF}(id_i, t) > \tau \} \]

\section{Consensus Function}
Weighted voting:
\[ V_t = \frac{\sum w_{i,t} \cdot v_{i,t}}{\sum w_{i,t}}, \quad w_{i,t} = w_i \cdot r_i(t) \]

\section{Reputation Dynamics}
\[ r_i(t+1) = r_i(t) + \alpha C_i - \beta F_i \]

\section{Adversarial Model}
Bounded adversary can inject false data, create Sybil nodes, corrupt votes, but cannot break VRF or hash functions.

\section{Theoretical Properties}
\textbf{Theorem 1.} History chain is tamper-evident under collision-resistant hash.
\textbf{Theorem 2.} VRF ensures committee unpredictability.
\textbf{Theorem 3.} Sybil influence is probabilistically bounded.
\textbf{Theorem 4.} Weak convergence when honest weight > 1/2.

\section{Live Evaluation}
Five live integration tests were performed with Grok and Claude, covering multi-agent AI safety, healthcare diagnostics, DeFi trading, and BGP peering scenarios. All tests successfully demonstrated detection, isolation of malicious actors, and preservation of a verifiable immutable decision trace.

\section{Implementation}
Reference implementation combines Go (distributed layer), Rust (SAIL adversarial kernel), and Python SDK for universal LLM integration.

\section{Difference from Existing Systems}
GQRVP is neither a blockchain, nor a database, nor a pure LLM system — it is a verifiable epistemic evolution system under adversarial conditions.

\section{Limitations}
Probabilistic guarantees, simplified adversarial model, no economic incentives yet.

\section{Future Work}
Full BFT formalization, game-theoretic incentives, zk-based verification, large-scale deployment.

\section{Conclusion}
GQRVP, integrated with multiple LLMs including Grok, demonstrates a new foundation for trustworthy AI and distributed systems where truth emerges from survival under attack and is preserved immutably for future generations.

\end{document}
